Bow shocks, bow waves, and dust waves

### 2019-02-21 papers/Papers1234/sec-dust-bow-discuss.tex
Start caption for mass-loss figure

Rather than clutter the diagram with error bars, we instead show the
sensitivity to observational errors in the lower-right gray box, where
each arrow corresponds to a factor of two increase (0.3~dex) in an
observational quantity: distance, \(D\); stellar luminosity, \(L_*\);
total infrared flux, \(F_{\text{IR}}\); and bow angular apex distance,
\(\theta\).  Most sources are members of known high-mass clusters with
distance uncertainties less than 20\% (0.08~dex).\footnote{The only
  exception is Source~329 in Cygnus, for which the distance
  uncertainty is roughly a factor of 2 \citep{Kobulnicky:2018a}.}  The
stellar luminosity is determined from spectral classification, which
makes it independent of distance.  Taking a \SI{2000}{K} dispersion in
the effective temperature scale \citep{Martins:2005a} gives an
uncertainty of 25\% in the luminosity, and adding in possible errors
in gravity and the effect of binaries, we estimate a total uncertainty
in \(L_*\) of 50\% (0.45~mag or 0.18~dex).  We estimate the
uncertainty in shell bolometric flux, \(F_{\text{IR}}\), by comparing
two different methods: model fitting \citep{Kobulnicky:2017a} and a
weighted sum of the 8, 24, and \SI{70}{\um} bands
(App.~\ref{app:bow-shock-data}), giving a standard deviation of 17\%
(0.07~dex).\footnote{%
  The absolute flux calibration uncertainty for both Herschel CAPS
  \citep{Balog:2014a} and Spitzer MIPS \citep{Engelbracht:2007a} is
  less than 5\%.} %
For the angular apex distance, \(\theta\), the largest uncertainty for
well-resolved sources is due to the unknown inclination.
\citet{Tarango-Yong:2018a} show that the dispersion in true to
projected distances can introduce an uncertainty of \(30\%\)
(0.11~dex) in unfavorable cases (e.g., their Fig.~26).  For 5 of the
20 sources from \citet{Kobulnicky:2018a}, \(\theta\) is of order the
Spitzer PSF width at \SI{24}{\um}, so the errors may be larger.
Assuming all these observational errors to be independent yields a
total \(\pm 1~\sigma\) observational uncertainty shown by the blue
dashed ellipse in the figure.

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
  \caption{Mass loss rates}
  \label{fig:mass-loss-vs-luminosity}
\end{figure*}

>>>>

Rather than clutter the diagram with error bars, we instead show the
sensitivity to observational errors in the lower-right gray box, where
each arrow corresponds to a factor of two increase (0.3~dex) in an
observational quantity: distance, \(D\); stellar luminosity, \(L_*\);
total infrared flux, \(F_{\text{IR}}\); and bow angular apex distance,
\(\theta\).  Most sources are members of known high-mass clusters with
distance uncertainties less than 20\% (0.08~dex).\footnote{The only
  exception is Source~329 in Cygnus, for which the distance
  uncertainty is roughly a factor of 2 \citep{Kobulnicky:2018a}.}  The
stellar luminosity is determined from spectral classification, which
 makes it independent of distance.  Taking a \SI{2000}{K} dispersion in
the effective temperature scale \citep{Martins:2005a} gives an
uncertainty of 25\% in the luminosity, and adding in possible errors
in gravity and the effect of binaries, we estimate a total uncertainty
in \(L_*\) of 50\% (0.45~mag or 0.18~dex).  We estimate the
uncertainty in shell bolometric flux, \(F_{\text{IR}}\), by comparing
two different methods: model fitting \citep{Kobulnicky:2017a} and a
weighted sum of the 8, 24, and \SI{70}{\um} bands
(App.~\ref{app:bow-shock-data}, eq.~[\ref{eq:total-ir-flux}]), giving
a standard deviation of 17\% (0.07~dex).\footnote{%
  The absolute flux calibration uncertainty for both Herschel PACS
  \citep{Balog:2014a} and Spitzer MIPS \citep{Engelbracht:2007a} is
  less than 5\%.} %
For the angular apex distance, \(\theta\), the largest uncertainty for
well-resolved sources is due to the unknown inclination.
\citet{Tarango-Yong:2018a} show that the dispersion in true to
projected distances can introduce an uncertainty of \(30\%\)
(0.11~dex) in unfavorable cases (e.g., their Fig.~26).  For 5 of the
20 sources from \citet{Kobulnicky:2018a}, \(\theta\) is of order the
Spitzer PSF width at \SI{24}{\um}, so the errors may be larger.
Assuming all these observational errors to be independent yields a
total \(\pm 1~\sigma\) observational uncertainty shown by the blue
dashed ellipse in the figure.

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{figs/Mdot-vs-lum-combo-edited}
  \caption{Wind mass-loss rates as a function of stellar luminosity,
    derived from (a)~our momentum efficiency method and (b)~the grain
    emissivity method of \citet{Kobulnicky:2018a}, with corrections as
    described in Appendix~\ref{app:bow-shock-data}.  Circle symbols
    show the sources from K18, colored according to the stellar
    effective temperature (see key at far right). }
  \label{fig:mass-loss-vs-luminosity}
\end{figure*}
